\section{Publication and Speakers Council}
\label{sec:pub}

%\textcolor{red}{To be filled in by Publications WG}. 

\Comment{Formal Publication and Speakers Bureau Policy - 2nd draft}

The policy below is a draft formal bylaws.  It is not a consensus document of the Interim Publications Working Group.  It is meant to be a complete, self-consistent policy to spur discussion and gather thoughts and suggestions about how the pieces need to work together. Points below that especially warrant further discussion or may be controversial are marked in red. The policy attempts to lay out the various responsibilities of publication board and speakers bureau members, working group coordinators, as well as relationships to other parts of the collaboration structure, like the governing board  and membership committee. These responsibilities could be redistributed in different ways. What projects/paper are ``Key," and get alphabetical author lists, if we adopt that model, is a point of contention, and we fill seek further input from the collaboration. We consider several possibilities for Key topics at the very end.

%CMB-S4 publication and talks bylaws Established March 2018

\subsection{Principles}
This policy seeks to ensure an equitable distribution of credit for work in the CMB-S4 Collaboration, to encourage and incentivize active work by collaboration members, and to ensure the resulting publications are of high quality. The authorship policy of the American Physical Society (2002) states: \textit{``Authorship should be limited to those who have made a significant contribution to the concept, design, execution or interpretation of the research study. All those who have made significant contributions should be offered the opportunity to be listed as authors.''}\footnote{\url{https\://www.aps.org/policy/statements/02\_2\.cfm}}

The Publication Policy will apply to all projects and publications that employ collaboration resources, including unreleased data, simulation codes and products, hardware and software
engineering designs, and analysis pipelines. All CMB-S4 collaboration members agree to the publication policy upon joining, and if they leave the collaboration, they are bound by it for two years afterward.

\subsection{Organization}
The execution of the policy shall be overseen by a Publication and Speakers Board chaired by an elected representative from the Executive Board.  There are two sub-committees: the Publications Board with eight collaboration members and the Speakers Bureau with four collaboration members. Roughly half of each group should be pre-tenure. The Governing board shall appoint members to these positions for staggered two-year, non-consecutive terms. The collaboration Spokesperson(s) will also help to navigate and resolve potential conflicts. The Science Council approves the projects that lead to publications. The Membership Board will keep track of active collaboration members and legacy member for the purposes of establishing author lists for papers.

\subsection{Project Proposal Process}

\Comment{[Ed. note: The entire concept of ``Key Science" papers is up for discussion, but only bits are highlighted below to avoid making the whole paragraph red.  Such a concept (under various names) is employed is many collaborations.  At the very end, we place possible suggestions for ``Key" topics.]}

Any collaboration member may propose a collaboration research project to an appropriate Science or Technical Working Group.  Such a project is work that is intended to result in a journal publication after a fixed term, or a small set of related publications.  There are three categories for projects:
Projects that are designated as ?Key Projects? represent the main science goals of the CMB-S4 collaboration (or forecasts for what we will achieve), where the collaboration must speak with a single voice.  
?Standard? analysis projects represent other science goals and use collaboration science data.  
Other forecasts and technical reports are collaboration-vetted projects that do not require collaboration science data and may lead to a publication or conference proceeding.  
The Science Council will maintain the list of Key Science topics, established prior to any projects being initiated.  Topics can be added to the Key Science Paper list and reviewed in coordination with the Publication Board.

The Publication Board will establish the template for project submission.  The project proposal document will designate a project leader and team, and describe the project, its estimated completion date, and final products.  Work on collaboration data should apply toward a collaboration project: failure to submit a project at its initiation, or writing a paper on internal collaboration data for submission when the data become public, will be considered a violation of the policy.  The same general type of analysis on subsequent observing seasons or data releases will be considered separate projects.  After discussion, resolution of conflicts, and consensus within the Working Group, the Working Group Coordinators will submit the project to the Science Council with a project category recommendation as a Key project, standard project, or theory forecast / technical report.  At this time the working group coordinators will announce the proposal to the Collaboration for a two-week consideration period, for discussion and further resolution of conflicts.  Addressing overlap between projects may require revision of the proposed project, and will be negotiated by the Working Group coordinators, Project Leaders, and Spokesperson(s).  Teams should welcome to join any colleagues that wish to make a defined and useful contribution to the project.

The Science Council may then approve the project or send it back to the Working Group for further revision.  In the event of a tie vote in the Science Council, the collaboration spokesperson  will cast the deciding vote.  When approved, the Publication Board will record the proposal in its project database.  Once recorded, the collaboration may not re-classify a standard project as key without the written agreement of all named project team members.  If there is any substantial change in the scope of a project as it matures, the Project Leader should adjust the project description accordingly, which will result in a new announcement and opportunity for collaboration review.

Projects led by thesis students will be given special consideration to protect them from competition within the collaboration.  Projects that require joint work with an external collaboration will require a memorandum of understanding set up by the Governance Board that specifies authorship and publication policies for that work.  These should be as compatible as possible with the respective collaboration policies.  Projects may add individual external collaborators to the team provided that no unreleased data is provided to them.

Project teams have the responsibility to carry projects to completion and publication.  The Publication Board will query the working group coordinators twice yearly for progress reports on all projects, and forward the results to the Science Council.  Any projects without progress for one year will be noted as ?inactive? and will be dropped from the database if there is still no progress at the next review.

\subsection{Authorship}
\Comment{[Ed. note: Aside from the concept of ``Key science" vs ``standard papers," the main dispute in this section relates to opt-in/opt-out as the default, or whether a weak opt-in is any better than an opt-out.]}

The three types of projects differ in their authorship rules.

For Key papers, all active members of the collaboration and all legacy members will automatically be placed on the author list.  The author list will start with ?The CMB-S4 Collaboration? and otherwise be alphabetical with the Project Leader designated as the corresponding author.  The Membership Board will provide the current list of eligible active and legacy members to the Publication Board, who will maintain an online process for members who choose to opt out of the paper.
For standard papers, the author list will be two-tiered.  The first tier will typically consist of untenured (or equivalent) members of the project team, ordered according to their preference.  (The publication panel can allow exceptions for senior scientists in the first tier in rare cases when justified by their contribution.)  The project leader will typically be the first author.  The second tier will consist of all active members and legacy members that choose to opt in online after an email notification.  The final line of the author list will be ?The CMB-S4 Collaboration?
For other forecasts and technical reports, the author list will consist of the project team only, plus any collaboration members that contributed to the study, as determined by the project team and appropriate working group coordinators, unless those author opt out.  The author list should be ordered according to the preference of the project team, followed by ?for the CMB-S4 Collaboration.?  For conference proceedings, the author list may be the single person who presented.

Any disputes regarding authorship will be resolved by the Publication Board with the Spokesperson providing a tie-breaking vote if necessary.  If an eligible member is unable to opt in, due to an unforeseen circumstance, the Publication Board may add them to the author list.

\subsection{Collaboration Review and Paper Submission Process}
\Comment{[Ed. note: the timing of the formation of the review team with respect to collaboration-wide review is a point of debate.  Some feel that the reviewers should be assigned early, so that they can iterate more with the authors on the paper.  Others feel the assignment of the editors should only happen at the beginning of the collaboration-wide formal review, otherwise the review process is too closed and not democratic.  The scheme below has a mix of these features.]}
 
The project leader and the project team have the responsibility to draft the publication based on their research.  All collaboration papers will have a title following the template, ?CMB-S4: <results of amazing research>.?  These papers will be developed in coordination with the relevant working groups, and kept in a repository that is visible to the whole collaboration.  Any collaboration member may comment on the project at any time.  When the paper matures to an advanced draft, the working group coordinators will request that the Publication Board form an internal review committee.  

This internal review committee consists of a primary and a secondary reviewer who have the responsibility that the collaboration?s publications are of uniform and high quality.  The reviewers are not current members of the Publication Board, but the Publication Board assigns one of its members to oversee the review of the paper as a rapporteur.  At least one of the reviewers or rapporteur should be a senior scientist who can insulate junior participants (whether authors, reviewers, or rapporteurs) from unfair criticism, if it occurs.

The Publication Board will notify the full collaboration that the internal review committee has formed.  Collaboration members may comment on the draft at any time, but when the authors are ready, the Publication board will sent announcement of a formal three-week comment period.  After the this comment period, the reviewers will provide a written report on the paper to the authors and Publication Board.

All public comments, from collaboration members and from reviewers, are to be posted to a centralized location maintained by the Publication Board, along with the authors? responses.  All collaboration members have access to these previously asked questions and responses.

The working group coordinators and rapporteur oversee iterations on the draft.  When the reviewers, working group coordinators, and rapporteur are satisfied that comments have been appropriately addressed, they present the paper to the Publication Board, who gives final permission and sets the date for paper submission.  The submission date is announced to the collaboration with a notice for final reading.  

In total, all projects/papers will have four formal public announcements to the collaboration: (1) when proposed, (2) when the review committee forms, (3) when the formal comment period begins, and (4) when the call goes out for final reading before submission.  Projects will also naturally be discussed in plenary teleconference calls, progress reviews, and working group reports.

All CMB-S4 publications, including proceedings and theses, must include a standard acknowledgment, agreed to and updated by the Governing Board, and made available by the Publication Board.  The CMB-S4 Collaboration will pay the page charges for Key papers. For all other papers, the page charges are the responsibility of the authors.

Any disputes regarding the review process will be resolved by the Publication Board with the Spokesperson providing a tie-breaking vote if necessary. In the case of a time-sensitive discovery, the review period may be shortened by unanimous consent of the Publication Board.

Graduate Thesis and dissertation documents are exempted from collaboration review, but related publications (e.g. developed from an individual chapter) are subject to review.

\subsection{Talks and Public communications}
\Comment{[Ed. note: This is based on the non-controversial interim policy.]}

The role of the Speakers Bureau is to help collaboration members give more and better talks in support of the CMB-S4 collaboration. The duties of the Speakers Bureau are to:
Solicit invitations to conferences and identify good venues for contributed talks.
Actively solicit speakers for invitations or notable conferences with no volunteer speakers. Priority and consideration should be given to the teams from projects where alphabetical author lists may obscure their role. 
Promptly respond to requests for speakers from conference organizers and act a point-of-contact for people who want some CMB-S4 speaker but do not have specific ideas.
Curate a library of standard plots and slides for speakers to use in talks.
Maintain a library of past CMB-S4 talks.
Address overlap from multiple requests to give talks on the same subject at the same conference, ideally by suggesting focus changes to make them on different topics. Talk prioritization will be at the committee's best judgment, but should reflect contributions to the topic in question, career status, whether the speaker was invited, and other similar factors.

To give a talk, whether contributed to a conference/workshop or invited,  a collaboration member must notify the speakers bureau. This ensures that the speakers bureau has a chance to address overlapping talk request or, in the case of declined invitations, can locate another appropriate speaker.  The talks policy applies to all workshops, meetings, colloquia, public lectures, and seminars.  The policy does not apply to talks on other subjects that contain brief advertisements for CMB-S4 (this is highly encouraged), to invited presentations that must remain confidential for programmatic reasons (e.g. certain agency reviews or presentations to private foundations or donors), or to informal presentation at collaboration members home institutions.  

All talks must maintain confidentiality for the project. For all talks except those exempted in above, collaboration members must send abstracts and titles to the collaboration at least three days prior to submission, or as soon as possible in the event of last-minute invitations. Slides must be sent to the collaboration at least one week before being presented and should include ``for the CMB-S4 collaboration" on the title slide.

Unpublished results shown in talks, including those talks exempted in above but not including thesis defenses, must be approved for public release by the collaboration before being shown. Such results should be marked ``CMB-S4 PRELIMINARY" on slides until publication.  Final public oral presentations for thesis student are not bound by the speakers policy and may show unreleased data, but must maintain confidentiality of major results.

The Speakers Bureau will maintain records of all presentations given in the name of the collaboration, and serve as a clearinghouse for talk invitations forwarded from any member.  

\subsection{Violations of the Policy and Remedies}
Violations of the policy will be addressed by the Publication Board, which will recommend a remedy to the Governance Board.  Minor infractions will receive a warning, while repeated or severe infractions may warrant suspension from project teams or working group activities, removal from such groups, or expulsion from the collaboration, as determined by the Governance Board.

\subsection{Amendments}
Any collaboration member can propose an amendment to the Publication/Speakers Policy. The Publication and Speakers will jointly discuss the amendment and forward a recommendation to the Governance Board for a final, majority vote.









\subsection{Key Science Topics}
\Comment{[Ed. note: below are various suggestions for topics that could be considered ?Key? papers and given alphabetical author lists.  They are organized from narrow to broad scope, where the broadest scope includes all science with CMB-S4.]}

\subsubsection{Proposed list of Key Science topics (Super narrow scope)}

(Idea is ``achieved S4 science target from Science book or detection")

Overview Papers

Data release of maps

B-mode detection or achieved S4 science target

Neutrino mass detection or achieved S4 science target

Neff detection or achieved S4 science target

Dark matter detection or achieved S4 science target 

New highly-significant discovery, such as a new planet

\subsubsection{Proposed list of Key Science topics (Narrow scope)} 

(Idea is ``new measurements from Science book")

Overview Papers

Data release of maps

B-mode limits (e.g. updated annually) or detection

Neutrino mass limits or detection

Neff limits or detection

Dark matter limits or detection (axion isocurvature, etc.)

New highly-significant discovery, such as a new planet

\subsubsection{Proposed list of Key Science topics (Broad scope)}

(Idea is ``all data products")

Overview Papers

Data release of maps

T/E/B Power Spectra (including B mode limits/detection)

Lensing Potential Map and Power spectra

Release of Likelihood

Cosmological Parameters (including all neutrino mass, Neff, dark matter limits/detections)

Galaxy Cluster Catalog

Point Source Catalog

Alternatively, Key Science topics could include almost everything (Broadest scope)
(Idea is ``all data products and all science from the sky")
Still excluded could be technical papers and lab-characterizations of equipment



%\subsection{Scope}
%The authorship policy spells out the criteria and procedures for determining which members of the collaboration will be listed as authors on publications. The author list will be comprised primarily of currently active members of the collaboration that satisfy the effort and shift criteria discussed below. Former members of the collaboration that have recently left can also opt to be included as legacy authors. Procedures for adding special cases and for addressing appeals are also specified. The formulation of the author list is treated separately for physics papers and technical papers. In general, the author list for a given paper is considered frozen once the paper has been submitted. Exceptions to this are discussed in Section~\ref{sec:except}.


%\subsection{Current Authors}
%Current authors are scientists at the level of graduate student or above who are members of the CMB- S4 collaboration and are actively engaged in the collaboration. This includes visitors. They will have contributed a significant fraction of their research time to the collaboration in the twelve months prior to preparation of the author list.

%The initial set of proposed authors will be submitted to the IB by each of the IB representatives, who will prepare a list of proposed names at their institution, along with a brief description of their contributions and level-of-effort. The IB chair will circulate this initial list to the IB one month in advance of the vote. IB members who want a specific candidate discussed will submit the name of the candidate to the IB chair no less than two weeks before the vote, with any questions or issues, and that name will be flagged for discussion.

%The IB chair will send the names, questions and issues regarding these candidates to all IB representatives promptly. At the initial vote, candidates who have not been flagged can be accepted by acclamation; flagged names will be discussed individually with the IB representative making the case for the candidate. A majority vote of voting members will suffice to include the candidate. This group will form the default author list for all qualifying CMB-S4 publications as defined in Section~\ref{sec:pubdef}. Individual authors can opt out of being included as an author for a given publication by notifying the spokesperson.

%The current author list will be updated through this mechanism as appropriate but at least once per year, with the IB chair supervising the update. For the updates, the IB representatives will flag any new additions to the author list. Once formed, the current author list will be made available to the collaboration. Any individual member of the collaboration can petition the chair of the IB for inclusion if they believe to have been improperly excluded.

%\subsection{Voting Rules}

%A majority vote of those voting is required, and all authorship votes follow this rule unless otherwise noted.

%\subsection{Definition of Qualifying Publications}

%The current author list shall be attached to any publication, as defined in Section~\ref{sec:pubdef}, discussing a physics result, as defined in Section~\ref{sec:pubdef}. In addition, when allowed, it shall also be attached to conference proceedings.

%\subsection{Legacy Authors}
%Legacy authors are individuals who have ceased active participation in the collaboration preceding submission of a publication but choose to opt-in to the author list via email to the spokesperson. The opt-in can either be a blanket opt-in, whereby the individual?s name is automatically included in the author list for all papers, or a case-by-case opt-in, whereby the individual must contact the spokesperson for each submitted paper. An individual can exercise his or her opt-in option until their legacy period has expired. For deceased members, the blanket opt-in option will be assumed. The legacy period, which applies to visitors as well, will be set to either one year or one-quarter of the time since the person has joined the collaboration, whichever is longer. The time a person joined shall be taken from the collaboration list as maintained by the IB chair. Once the legacy period has expired the Special Author rules apply.

%\subsection{Special Authors}
%Special authors are defined as authors who do not qualify as current or legacy authors but are listed on an individual paper based on specific contributions to that paper. Engineering staff, technicians, undergraduates, and other non-physicists who have made exceptional contributions are examples of special authors, as well as scientists who have made significant contributions to the specific paper. They must be nominated for inclusion on the author list by a member of the IB.

%Visitors, whose contact with the collaboration may encompass a period of less than one year, may be accepted as authors on papers concerning topics to which they have made significant contributions, subject to the legacy period and the approval of the IB.

%For the first paper reporting, CMB-S4 individuals can either be nominated by a member of the IB, or can petition the IB chair for inclusion on the author list. In either case, both of the following conditions must be met: (1) the individual must have worked on the collaboration for at least one FTE year, and (2) the individual must have made an intellectual contribution to the collaboration. The IB must approve special author nominations and petitions by a majority vote.

%\subsection{Technical Publication Authors}

%Publications that discuss technical results, as defined in Section~\ref{sec:pubdef}, will not be required to carry the current author list. Publications in NIM, IEEE, SPIE on hardware, or specialized simulations are typical examples. The primary proponents of technical papers will create a custom author list that does not require approval of the collaboration. However, the draft manuscript must be submitted to the Publications Board (cf. Section~\ref{sec:pubdef}) and the author list to the IB. IB representatives can ask the proponents to add individuals they think ought be included on the author list.

%\subsection{Examples of Contributions Qualifying for Authorship}

%The following list gives examples of contributions; it is meant to be indicative, not exclusive, and to serve as a guideline:
%\begin{itemize}
%\item governance of the collaboration
%\item construction of the experiment
%\item maintenance or operation of the experiment ? scientific effort during the project phase
%\item simulation or data reconstruction work
%\end{itemize}
